Correctly Optimizing Abstract Abstract Machines

### 2013-03-29 paper/paper.tex
Summary of results.

>>>>

Our step-wise optimizations strictly produce better analysis times
with no observed loss of precision.  The final result is a
systematically derived and verified implementation that operates
within a small factor performance loss compared to a hand-optimized,
unverified implementation.  Moreover, much of the performance gains
are achieved with purely functional methods, which suggest potential
further gains from parellelization.  Peak memory usage is often
considerably improved by the end of the optimization steps, but the
effect of mutation has unexpected consequence on the analyzers memory
consumption.
